---
title: "COVID Exploration"
author: "Ryan Harrington"
date: "11/8/2021"
output: 
  html_document:
    theme: yeti
    highlight: textmate
    toc: TRUE
    toc_float: TRUE
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)

source(here::here("functions.R"))

theme_set(theme_minimal())
```

# Read in Data

## Read in data

```{r}
# Link for confirmed cases
confirmed <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"

# Link for confirmed deaths
deaths <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"
```

```{r}
confirmed_df <-
  read_csv(confirmed) %>% 
  mutate(Type = "Confirmed")

deaths_df <-
  read_csv(deaths) %>% 
  mutate(Type = "Deaths")
```

## Create a population dataframe

```{r}
population_df <- 
  deaths_df %>% 
  select(UID, iso2, iso3, code3, FIPS, Admin2, Province_State, Country_Region, Lat, Long_, Combined_Key, Population)
```

## Add population to confirmed

```{r}
confirmed_df <-
  confirmed_df %>% 
  left_join(population_df,
            by = c("UID", "iso2", "iso3", "code3", "FIPS", "Admin2", "Province_State", "Country_Region", "Lat", "Long_", "Combined_Key")
  ) %>% 
  select(UID, iso2, iso3, code3, FIPS, Admin2, Province_State, Country_Region, Lat, Long_, Combined_Key, Population, everything())
```

## Union confirmed cases and deaths together

```{r}
covid <- 
  union(confirmed_df, deaths_df) %>% 
  select(UID, iso2, iso3, code3, FIPS, Admin2, Province_State, Country_Region, Lat, Long_, Combined_Key, Type, Population, everything())
```

# Check County Data

## New Castle

```{r}
covid %>% 
  filter(Admin2 == "New Castle")
```
## Kent

```{r}
covid %>% 
  filter(Admin2 == "Kent",
         Province_State == "Delaware")
```

## Sussex

```{r}
covid %>% 
  filter(Admin2 == "Sussex",
         Province_State == "Delaware")
```

## Delaware

```{r}
covid %>% 
  filter(Province_State == "Delaware")
```

# Toy functions

## Tell me today's date

### With explicit return

```{r}
tell_me_todays_date <- function() {
  
  # Body of the function
  todays_date <- format(Sys.Date(), format = "%B %d, %Y")
  
  sentence <- paste0("Hello! Today's date is ", todays_date, "!")
    
  return(sentence)
  
}
```

### With implicit return

```{r}
tell_me_todays_date <- function() {
  
  # Body of the function
  todays_date <- format(Sys.Date(), format = "%B %d, %Y")
  
  paste0("Hello! Today's date is ", todays_date, "!")
  
}
```

```{r}
tell_me_todays_date()

tell_me_todays_date()
```

## Distance from the mean

```{r}
set.seed(1231)

nums <- sample(1:100, 25, replace = T)

nums


nums - mean(nums, na.rm = T)
```

```{r}
calc_mean_dist <- function(values) {
  
  dist <- values - mean(values, na.rm = T)
  
  return(dist)
  
}
```

```{r}
calc_mean_dist(values = nums)
```


```{r}
calc_mean_dist(1:10)
```

```{r}
calc_mean_dist(seq(from = 1, to = 173, by = 5))
```

# Function for filtering counties

```{r}
get_county(covid, "New Castle")
get_county(covid, "Kent")
get_county(covid, "Sussex")
get_county(covid, "All counties")
get_county(covid, "All counties", "Maryland")
```

# Continue with Data Cleaning

```{r}
covid %>% 
  get_county("New Castle") %>% 
  tidy_covid()
```

```{r}
covid %>% 
  get_county("Kent", "Maryland") %>% 
  tidy_covid()
```

```{r}
covid %>% 
  get_county("Monmouth", "New Jersey") %>% 
  tidy_covid()
```

```{r}
covid %>% 
  get_county("All counties") %>% 
  tidy_covid()
```

# Adjusting from cumulative to daily values

```{r}
covid %>% 
  get_county("All counties") %>% 
  tidy_covid()
```


# Graphing our data

```{r}
covid %>% 
  get_county("All counties") %>% 
  tidy_covid() %>% 
  ggplot(aes(x = Date,
             y = Confirmed,
             color = Admin2,
             group = Admin2)) +
  geom_line() +
  scale_y_continuous(labels = scales::comma) +
  theme(legend.position = "top",
        axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "italic")) +
  labs(color = "")
```

```{r}
covid %>% 
  get_county("All counties") %>% 
  tidy_covid() %>% 
  graph_covid_over_time(Confirmed_DoD)
```



